\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cs_hw}

\pagestyle{fancy}

\begin{document}\thispagestyle{empty} % No header on first page
\maketitle
\te{p3} is the giant of the 15-410 experience, and one of the largest
projects you'll ever do at CMU in a class. While the assignment's individual
parts aren't that hard, choosing the wrong design, and making poor choices
throughout the project can lead to devastating outcomes, since large amounts
of code is very difficult to fix and mistakes are amplified over time as you
do the project.

The project handout from the 15-410 course staff compiles some warnings from
previous semester, but I feel like there can be a bit more detail for certain
parts. I will detail some parts of the handout I think deserved more
attention, and hopefully it will help you as well when you undertake the
\te{p3} experience.

\section{Relationship between \te{p2} and \te{p3}}
Maybe it's obvious, but when I started \te{p3} I wasn't sure about the
connection between \te{p3} and \te{p2}. Of course, \te{p2} is user space
code, and \te{p3} is kernel space code, but it seems like you might want to
run user space code with kernel code, right?

In \te{p2}, you wrote user code that ran on top of a kernel that was already
written for you. That way, you didn't have to worry about the kernel at all.
In \te{p3}, you are implementing that kernel that ran under your user code.
When you are running your kernel in \te{p3}, for the most part, you don't
have to worry about your \te{p2} code. The only thing is probably your
\te{install\_autostack} (see Plan of Attack \ref{tip:autostack}), which is
called on the entry of every program.

What this means, is things like the locks you wrote in \te{p2} cannot be used
by your \te{p3} kernel. This means you will have to rewrite another
\te{panic}, and rewrite locks for your \te{p3} kernel.

When you start testing more advanced programs later on, you can run \te{p2}
code on top of your \te{p3} kernel, and see if things still work the way you
expect.

\section{Error Checking}
\label{sec:error}
In class, they introduce why error checking is important and how you should
go about handling errors in your code. The main lesson learned from class
however, is that
\begin{equation}
  \te{No error should be left unheard}.
\end{equation}
That makes sense, and what this means to a lot of people is just to implement
the pass-the-buck error handling approach to everything.

However, the side that is not taught as much is how to actually handle these
error, and how to write assertions throughout your code to guarantee that it
is more safe.

Below, I'll outline the 3 most important error checking principles you should
utilize throughout your project.

You should keep in mind that although Passing the Buck and Assertions are two
strategies that you can actively implement in your code, \te{panic} is also a
powerful error checking tool. This means that you should \textbf{actively
consider all three methods of error checking}, without getting too hung up on
a particular method, just because it's easy to use or you understand it best.

\subsection{Passing the Buck}
As mentioned earlier, this is usually the easiest to understand method of
handling errors. The idea is that whenever something is wrong, you just
return a negative error code. Since there can be many different errors, you
should have different negative error codes for different errors. One approach
you can take is to have a bunch of defined error codes that are shared by
functions throughout your kernel.

\begin{lstlisting}[caption={Negative error code defines}]
  #define FUNCTION_ERRNO_NULL -1
  #define FUNCTION_ERRNO_INIT -2
  #define FUNCTION_ERRNO_ARGS -3
\end{lstlisting}

\subsection{Assertions}
While passing the buck is easy to implement, it can be weak since returning a
negative error code means you won't be able to pinpoint where the error is
until you have code that checks for a negative error code. For example, you
could potentially have a mutex init that fails, which gets passed up to a pcb
init, which then fails and is passed up to the kernel init function. You'll
know by the kernel init function that something went wrong, but you'll have
to track down some more to figure out when things \textit{really} went wrong.

A more specific error check you can do is an assertion, which course staff
sets up for you in \te{contracts.h}. Assertions are useful because when
something goes wrong, the exact line number will be returned to you at the
time of error. If you combined assertions with a good code tracing utility,
you can debug your errors much faster. In addition, assertions are good when
you have an error that you can't really recover from.

This is not to say an assertion is necessarily ``better'' than a passing the
buck error. For example, sometimes you may want the caller of the current
function to handle an error, which may be unrecoverable, in which case 
passing the buck is more appropriate than an assertion.

A good way to write your kernel is to write a bunch of assertions that
describe how you expect your function to behave, and fix things when
assertions start to break. This is actually a common practice in industry,
known as 
\href{https://en.wikipedia.org/wiki/Test-driven_development}
{TDD(Test Driven Development)}.
While this method of development can be rather slow, it can help you write
much more robust code, which is important for a project of this scale.

As an example, consider the following functions, one written entirely with
passing the buck, and the other with a mix in Listing \ref{lst:error_style}.
The \te{assertStyle} code is preferred here, since unrecoverable errors will
trigger the assertion error, helping you pinpoint errors, while errors that
are not as severe, for example passing in a bad value for a argument, are not
passed to the caller to handle.

\begin{lstlisting}[
    label={lst:error_style}, 
    caption={Comparing passing the buck and assertion styles}
  ]
  function buckStyle (int *apples, int pineapple) {
    if (apples == NULL) {
      return FUNCTION_ERRNO_NULL;
    }

    if (valid_mem(apples)) {
      return FUNCTION_ERRNO_MEM;
    }

    if (pineapple == 0) {
      return FUNCTION_ERRNO_ARGS;
    }

    apples += pineapple;

    return pineapple;
  }

  function assertStyle (int *apples, int pineapple) {
    ASSERT(apples != NULL);
    ASSERT(valid_mem(apples));

    if (pineapple == 0) {
      return FUNCTION_ERRNO_ARGS;
    }

    apples += pineapple;

    return pineapple;
  }
\end{lstlisting}

\subsection{\te{panic}}
I didn't do a whole lot of debugging in \te{p2}, so I didn't use panic. When
I got to \te{p3}, I didn't really know what it was for. In the handout, we
are told that \te{panic} is way to help us debug our code, and a good
\te{panic} function will help us debug faster. When I first heard that, I had
no idea what that meant...sounded like empty words to me.

The reason course staff is pushing you to write a \te{panic} function is
because of the following -- have you ever had the following scenario?
\begin{itemize}
  \item You run your program, and there's a bug
  \item You stop the execution, and look around the context
  \item Let me look at \te{\%esp, \%eip, \%cs, \%ss}... 
  \item Ok hmm...things look alright. Let me check the contents of the stack
  \item That seems fine...let me look at the parameters of the current TCB
  \item Alright, I'm curious what tasks are currently scheduled in the
  scheduler. Ugh...this is going to be a lot of \te{simics psym} commands.
  \item Oof, I also want to see what threads are current sleeping.
  \item Hmm...would also be nice to know how many free pages I current have.
\end{itemize}
The above debugging journey is not necessarily hard to do, but it is
certainly \textit{time consuming}. Typing in \te{simics} commands is quite
unwieldy, and is also limited in what you can do. A \te{panic} function can
help you do all these things in one go. Something goes wrong -- \te{panic}!
Everything you want to know in general can be printed out, from the current
task, to the tasks in the scheduler, the current timer stats, the context on
the surrounding stack area -- literally anything you deem useful. Since your
error-checking code, like \te{ASSERT}, will call \te{panic}, every time
something goes wrong, you'll automatically be able to get a printout of what
happens. You can even implement checks in your \te{panic} to automatically
check certain sanity things for you, for example if your segment registers
make sense or the program instruction pointers are reasonable.

Some features you might consider putting into your \te{panic}:
\begin{itemize}
  \item Print out the current state
  \begin{itemize}
    \item Registers
    \item Any state variables stored in the kernel
    \item Surrounding stack near the \te{\%esp}
    \item Surrounding stack of the user program, if applicable
  \end{itemize}
  \item Print out the current TCB 
  \item Print out the current PCB
  \item Print out some tasks in the scheduler's active, sleep queues
  \item Print out global variables
\end{itemize}

\section{Locking}
\label{sec:locking}
One trap I fell into while doing \te{p3} was that I wanted to get everything
working with \te{disable\_interrupts} before continuing with locking. While
this will definitely help you finish your project, it will probably not let
you integrate locking into your project enough to the point where you can
have a kernel with many interleaving threads with no race conditions.

My suggestion is, by the time you've coded up your TCB, PCB structures, you
should strive to not disable interrupts on any syscall. Of course, it's ok to
disable interrupts during debugging and other intermediary developments, but
you should strive to be able to reach checkpoints where all your syscalls
don't have to disable interrupts.

A good start for locking is to port all the fundamental locks you created in
\te{p2} -- your \te{mutex}, \te{cond}, \te{sem}, \te{rwlock} -- so this way
it will encourage you to use them where you feel fit. You will likely have to
slightly modify them a bit early on in your kernel, since you will likely not
be able to do things like deschedule yet, but that is ok. If you don't port
your locks over early on, locking will likely not be in your mind, so you'll
neglect it.

I would like to acknowledge that there are steps in the ``Plan of Attack'' of
the \te{p3} handout that try to push for this, but I feel like they aren't
explicit enough in what you should do to give you that push to put yourself
in a better position with the locking situation. Porting over the \te{p2}
locks I think is a great way to put yourself on the right track, and also
being extremely avoiding of \te{disable\_interrupts}.

\section{Plan of Attack Tips} There is a plan of attack section listed at the
end of the handout that gives a nice overview about what steps you should
approximately take to complete the project. Here are some additional tips,
not written in any particular order, that you should consider while working
on \te{p3}.

\begin{enumerate}
  \item Strive to document your code as you go. At the very least, make
  \te{doxygen} headers on all the functions and files you create, so you
  don't have to go through the pain of adding them in later on.
  
  \item One of the first things you should do is write all your system call
  and interrupt handlers. This includes exception handlers! They don't have
  to necessarily work yet (you can just \te{return} for now), However, if
  you're missing a handler and it gets triggered for whatever reason, you
  will get a mysterious \te{General Protection Fault}, since the handler is
  not installed in the IDT.
  
  You will probably find macros useful for installing all your interrupt
  handlers, since many handlers will share many parts. Early on though, you
  might want to just write it all out just because it's easier to do. There's
  not much documentation online about using macros in assembly, but using
  \te{\#define} is a simple way to implement macros for assembly, just like
  how you do for C code. There are some extra precautions you need to take
  though when defining macros for assembly.
  
  \item When they say to comment out some of your \te{install\_autostack}
  code, what you should understand is that for any program, the first
  function that is called is the function in \te{crt0.c}, which just performs
  the \te{install\_autostack} and then calls \te{exit} into the program you
  intended to execute. Therefore, since \te{install\_autostack} will be
  called by every program, and the function requires syscalls you may not
  have written yet, i.e. \te{new\_pages}, you will likely need to comment out
  most if not all of \te{install\_autostack}.

  \label{tip:autostack}

  \item They tell you to choose an error-handling approach early. When I
  originally read this, I thought they just meant to return various types of
  error codes. What I realized in retrospect was that you can use error
  checking to your advantage as you develop. See Section \ref{sec:error} for
  more details about how to use error checking as you write \te{p3}.

  \item They also tell you to think about locking early on. As mentioned in
  Section \ref{sec:locking}, you should port over all your locking constructs
  from \te{p2} early on, so you will think about locking early on in your
  project. This way, you'll be more encouraged to use locking when you find
  the chance, instead of feeling a big burden to port them over in the first
  place, and being distracted by trying to ``finish'' your kernel first with
  \te{disable\_interrupts} everywhere.
  
  \item If you are noticing that you are running a lot of the tests over and
  over again...especially the hurdle tests, it might be a good idea to write
  a program that runs suites of tests for you automatically. It'll save you
  time, and also encourage you to test more. One good practice when your
  kernel starts getting big is to run a set of tests every time you make a
  change, so if your change breaks something, you'll immediately know.
\end{enumerate}

\end{document}